Hillary Clinton Emails

### 2016-04-14 presentation/presentation.tex
add beginnings of code to make coefficient matrix

\begin{frame}{Latent Dirichlet Allocation: Some Details}
\begin{itemize}
\item Some questions we want to answer with LDA
\begin{itemize}
\item Can we see sensible topics in the LDA output?
\item What are the most common topics of the emails?
\item Who is associated most with each issue?
\item Do the topics proportions for each email line up with real world events?
\item Can we predict the source of a given email?
\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{Multinomial Logistic Regression}
\begin{itemize}
\item We next want to ask can we predict who said what?
\item To answer this question we employ multinomial regression.
\item We take a subset of people who sent emails, only those who have more that 100 emails sent and try prediction for these.
\end{itemize}
\end{frame}

@@

\begin{frame}{Conclusion}
\begin{itemize}
\item We've broken the corpus down to a level where we can effectively analyze it and draw conclusions using both human and statistical analysis
\item This has only been a sample of the many questions we could address using the LDA output
\item Possible future directions
  \begin{itemize}
  \item Some emails are redacted, how do email topics relate to this
  \item Correlation between topics, what topics appear together
  \item Predicting senders or receivers based on email text
  \end{itemize}
\end{itemize}
\end{frame}

>>>>

\begin{frame}{Latent Dirichlet Allocation: Some Details}
\begin{itemize}
\item Some questions we want to answer with LDA
\begin{itemize}
\item Can we see sensible topics in the LDA output?
\item What are the most common topics of the emails?
\item Do the topics for each email line up with real world events?
\item Can we associate email senders with topics?
\end{itemize}
\end{itemize}
\end{frame}

@@

\begin{frame}{Multinomial Logistic Regression}
\begin{itemize}
\item Can we do a better job associating email senders with topics?
\item To answer this question we employ multinomial regression.
\item We take a subset of people who sent emails, only those who have more that 100 emails sent and try to predict the sender using the topics.
\end{itemize}
\end{frame}

@@

\begin{frame}{Conclusion}
\begin{itemize}
\item We've broken the corpus down to a level where we can effectively analyze it and draw conclusions using both human and statistical analysis
\item This has only been a sample of the many questions we could address using the LDA output
\item Possible future directions
  \begin{itemize}
  \item Some emails are redacted, how do email topics relate to this
  \item Correlation between topics, what topics appear together
  \item Incorporating information on receivers 
  \end{itemize}
\item If this data intrigues you, all the code we used to download, process, and analyze the data is (will be) available at \url{https://github.com/lbybee/601_Final_Project}.
\end{itemize}
\end{frame}
